Planning helps ensure that transportation spending and policies
are as effective as possible. Since building infrastructure
is an expensive and time consuming deed, models
models which predict the impact of potential projects
or policies are used. The Traffic Equillibrium problem
is to find out the steady state usage of road network
infrastructure. This steady state usage is called
equillibrium of the network. Once this is obtained,
one can do a variety of things like redesigning the
road network to avoid congestion, set up tolls
to maximize profit, etc.. This chapter will introduce
the mathematical tools required to study the traffic
equillibrium problem. Further chapters states the equillibrium
problem formally and gives methods to compute the equillibrium.

\section{Representation of Transport Networks}
	The first step in finding equillibrium solution is to
	model the traffic network in a form that can be handled
	mathematically by a computer.
	Traffic network will be represented as a directed graph.
	Nodes in the graph would represent intersections and
	the \emph{edges/arcs/links} connecting the nodes represents
	the roadway connecting them.
	The nodes and arcs in the graph have various attributes
	like travel-time, distance, cost, number of travellers etc..

	Graph will be denoted as $G= G(N,A)$, where $N$ is the
	set of nodes and $A$ the set of links.
	A link from node $i$ to $j$ is represented as a
	tuple $(i,j)$ (or sometimes simply $ij$),
	where $i$ is the head node and
	$j$ is the tail node.
	A path in the network from node $r$ to node $s$
	is a sequence of links connecting $r$ and $s$.
	We will use the notation  $H_{rs}$ for the set of paths between
	$r$ and $s$, and $H$ for the set of all paths.


	\subsection{Travel Time Function}
	An interesting aspect of the transportation network is that
	the travel time along a link depends on the number of
	passengers traversing the link. The more crowded the link
	is, higher is the travel time. The travel time along a
	link could also depend on other factors like length of
	the link and the quality of road, etc.. Thus each link
	in the network has a travel time function associated
	with it, which is a function of the number of passengers in the
	link. Each link would also have a threshold on the maximum
	passengers it can hold. This is called the capacity of the
	link. We would want the travel time function of a link
	to blow up once the link exceeds its capacity. There are
	various functions that are used to model link travel times.
	The one we will be using is the \emph{Bereau of Public Roads}
	function (BPR function), which is given by:
	\[
		t(x) = t_0(1 + b(x/c)^{p})
	\]
	where $t_0$ is the free-flow travel time (travel time when
	the flow is zero). $c$ is the capacity of the link. $b$ and $p$
	are constant parameters that decide the nature of the link.

	\subsection{Demand and Flows}
	The number of passengers\footnote{A passenger in equillibrium analysis
	means one vehicle. But there are different kinds of vehicles
	with different sizes. These things are adjusted by
	multiplying a constant factor to the flow}
	in a link at a particular time
	is called the flow of the link. In practice, flow can take
	only integer value. But that would result in a discrete optimization
	problem, which are computationally difficult to solve. So we assume flows
	to be real valued. This significantly reduces the computational
	complexity of the problem and in fact reduces it to a convex
	optimization problem, which are computationally easy.

	Different nodes in the network will have different number of
	people travelling between them. A link connecting two major
	cities for instance will have more people travelling in it
	than a link between a city and a village.
	The number of people who travel from origin $r$ to destination
	$s$ on average is called the demand between $r$ and $s$. We
	will denote this by $d_{rs}$. A matrix containing demand information
	of all origin-destination pairs, $[d_{rs}]_{(r,s)\in Z^2}$,
	is called the \emph{OD matrix} or \emph{trip table}.


	\subsection{Shortest Paths}
	The shortest path problem is to find a path between given origin
	and destination with least travel time.
	In the problem of finding equillibrium flows in a traffic network,
	finding shortest paths between origin and destination pairs
	become a subproblem.
	There are many algorithms for finding shortest path in a graph.
	The one we will use is the well known \emph{Dijkstra's Algorithm}.
	The pseudocode for this is given in algorithm \ref{alg:dijkstra}.
	
	\input{introduction/dijkstra.tex}

\section{Overview}
The next chapter~\ref{chapter:math} recalls some facts
related to convex optimization
and mathematically states the definition of traffic equillibrium.
The chapter after that (chapter~\ref{chapter:alg}) discusses the four
algorithms, namely MSA, Frank Wolfe, Gradient Projection and
greedy method. The final chapter (chapter~\ref{chapter:results})
gives the results obtained after running the implementation of
these algorithms on real life networks.
