In this chapter we will discuss four different algorithms to solve
the Traffic Equillibrium problem. The first two generates
the equillibrium link flows and hence are called link-based
methods. The other two algorithms provide the equillibrium path
flows and are called path based methods.

All four algorithms proceed in a similar way. We start with
an initial feasible flow vector and update this vector until
equillibrium is attained. An important aspect that varies across
the algorithms is how the flow is updated. Different ways of
doing this makes one algorithm more efficient than the other.

Another key point is that due to errors in floating point operations,
it is impossible for the algorithm to converge exactly to the
equillibrium solution. Also for practical applications, it is
enough to obtain a solution which is reasonably close to the
equillibrium. Trying to obtain a higher precision would only
increase the run-time and yield no benefits.
This calls for a metric for how close the current solution is
close to equillibrium. We use \emph{Relativity Gap} to measure this.

\begin{definition}[Relativity Gap]
	Suppose $x$ is the current link flow solution vector. If $\hat{x}$
	is the all-or-nothing flow solution (i.e., all flow is
	assigned to the shortest path between each O-D pair), then
	the \emph{Shortest Path Travel Time}, SPTT is defined as
	\[
		\hbox{SPTT} = \sum_{ij\in A}t_{ij}(x_{ij})\hat{x}_{ij},
	\]
	\emph{Total System Travel Time}, TSTT is defined as
	\[
		\hbox{TSTT} = \sum_{ij\in A} t_{ij}(x_{ij})x_{ij},
	\]
	and finally, the \emph{Relativity Gap}, RG is defined as
	\[
		\hbox{RG} = \frac{\hbox{TSTT}}{\hbox{SPTT}}-1
	\]
\end{definition}

Observe that at equillibrium, RG must be equal to zero since all
used paths have minimal travel time. In the current implementations,
we have used $\hbox{RG}<10^{-4}$ as the stopping condition.


\section{Link Based Methods}
In the link flow methods, the link flows are
initialized to a feasible flow vector. This flow
vector is iteratively updated until equillibrium is attained,
making sure that the updated flows remain feasible
across the iterations.

In the current implementations, the initial feasible flow
vector is chosen to be the all or nothing assignment. The
pseudocode for the initialization is given in Algorithm~\ref{alg:initlink}.

\input{algorithms/initialize-link-flow.tex}

\subsection{Method of Successive Averages (MSA)}
\input{algorithms/msa.tex}

\subsection{Frank Wolfe}
\input{algorithms/fw.tex}

\section{Path Based Methods}
In path flow methods, the path flows are first initialized to a
feasible flow vector. This flow vector iteratively gets updated
till equillibrium is attained, making sure that the flow
vector remains in the feasible region.

Similar to the link based methods, the initial flow vector is
chosen to be the all or nothing solution, where all the demand
gets assigned to the shortest path. The pseudocode for initializing
path based methods is given in algorithm~\ref{alg:initpath}.
\input{algorithms/initialize-path-flow.tex}
\subsection{Gradient Projection}
\input{algorithms/gp.tex}

\subsection{Greedy}
\input{algorithms/greedy.tex}
